---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# slrPackage

<!-- badges: start -->
<!-- badges: end -->

The goal of slrPackage is to produce the main outputs that one would obtain by 
running the `lm` function on a simple linear regression model. This package contains
the single function `slr_output`.  

In order to run the function, the user would first input the predictor variable (x),
followed by the outcome variable (y), in the format of `slr_output(x, y)`.  

The slrPackage will then provide the following results:  
1. intercept (beta 0) and slope (beta 1) estimates  
2. standard error of slope (beta 1)  
3. f statistic and p value  
4. t statistic of slope (beta 1) and p value

## Installation

You can install the development version of slrPackage from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("clairekwl/625_slrPackage")
```

## Example

This is a basic example which shows you how to solve a common problem.  
We load the `iris` dataset from R. Suppose we want estimates for the following
SLR model:  
`Sepal.Length_i = Sepal.Width_i + e_i`

```{r example}
library(slrPackage)
## basic example code

# load sample R dataset
data(iris)
# running function: slr_output(predictor, outcome)
slr_output(iris$Sepal.Width, iris$Sepal.Length)
```
